### 2019-02-14 appendix_1.tex
fixes  of capacity constraints

\clearpage
\chapter{Landing time interval and AROT}\label{app:lti_and_arot}

@@

% Please add the following required packages to your document preamble:
% \usepackage{multirow}
% \usepackage{graphicx}
\begin{table}[h]
\centering
\resizebox{0.8\textwidth}{!}{%
\begin{tabular}{|c|c|c|c|c|c|c|c|}
\hline
\multicolumn{2}{|c|}{\multirow{2}{*}{RECAT-EU scheme}} & \multicolumn{6}{c|}{Follower}                   \\ \cline{3-8} 
\multicolumn{2}{|c|}{}& CAT-A & CAT-B & CAT-C & CAT-D & CAT-E & CAT-F \\ \hline
\multirow{6}{*}{\rotatebox[origin=c]{90}{Leader}}& CAT-A&& 100s  & 120s  & 140s  & 160s  & 180s  \\ \cline{2-8}
& CAT-B&&&& 100s  & 120s  & 140s  \\ \cline{2-8} 
& CAT-C&&&& 80s   & 100s  & 120s  \\ \cline{2-8} 
& CAT-D&&&&&& 120s  \\ \cline{2-8} 
& CAT-E&&&&&& 100s  \\ \cline{2-8} 
& CAT-F&&&&&& 80s   \\ \hline
\end{tabular}%
}
\caption[RECAT-EU time-based separation minima]{RECAT-EU WT time-based separation minima on approach and departure~\cite{rooseleer2015recat}}
\label{tab:RECAT-time}
\end{table}

>>>>

% \clearpage
% \chapter{Landing time interval and AROT}\label{app:lti_and_arot}

@@

% Please add the following required packages to your document preamble:
% \usepackage{multirow}
% % \usepackage{graphicx}
% \begin{table}[h]
% \centering
% \resizebox{0.8\textwidth}{!}{%
% \begin{tabular}{|c|c|c|c|c|c|c|c|}
% \hline
% \multicolumn{2}{|c|}{\multirow{2}{*}{RECAT-EU scheme}} & \multicolumn{6}{c|}{Follower}                   \\ \cline{3-8} 
% \multicolumn{2}{|c|}{}& CAT-A & CAT-B & CAT-C & CAT-D & CAT-E & CAT-F \\ \hline
% \multirow{6}{*}{\rotatebox[origin=c]{90}{Leader}}& CAT-A&& 100s  & 120s  & 140s  & 160s  & 180s  \\ \cline{2-8}
% & CAT-B&&&& 100s  & 120s  & 140s  \\ \cline{2-8} 
% & CAT-C&&&& 80s   & 100s  & 120s  \\ \cline{2-8} 
% & CAT-D&&&&&& 120s  \\ \cline{2-8} 
% & CAT-E&&&&&& 100s  \\ \cline{2-8} 
% & CAT-F&&&&&& 80s   \\ \hline
% \end{tabular}%
% }
% \caption[RECAT-EU time-based separation minima]{RECAT-EU WT time-based separation minima on approach and departure~\cite{rooseleer2015recat}}
% \label{tab:RECAT-time}
% \end{table}
